---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0.1
#ESSENTIALS
 author:
  - name: Hong Yun Ting
    email: ythong.2019@mitb.smu.edu.sg
    affiliation: Singapore Management University
  - name: Li ShuXian
    email: bob@example.com
    affiliation: Singapore Management University
  - name: Yang Xu
    email: xu.yang.2020@mitb.smu.edu.sg
    affiliation: Singapore Management University
main_findings:
  - "iSpy - An Interactive Visual Application for Exploring GAStech Employees Movement Data and Aliba, Kronos Events"
logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logocenter_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

# Introduction

The local company GAStech reported missing employees while multiple major outbreaks struck the city on the night of 23rd. To investigate the incidents, multiple sources of evidences have been collated:
1. GAStech released a tracking data of 2 weeks leading up to the disappearance as GAStech provides many of their employees with company cars for personal and professional use. GAStech also provided credit card transaction and Kronos-Kares loyalty card usage data.
2. Relevant microblog records that have been identified by automated filters and text transcripts of emergency dispatches by the Abila, Kronos local police and fire departments.


```{r, include=FALSE}
knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
```

## Objectives

1. To reveal city location hot-spots based on the spending data and to detect spending anomaly. Investigators are able to scale down the scope of analysis with more focus on specific segments with the use of selections. 
2. To create an interactive map visualization framework that supports selection of time frame as well as employees. Movement patterns of one or more employees are displayed to discover abnormal behaviors and unofficial relationships.
3. To build a timeline analysis for the chaotic night on 23rd based on text analytics. Leveraging on topic modelling techniques are extracted from the massive amount of text data to help investigators form better understanding on the occurrence of events.

# Methods

I will show here how to include poster elements that may be useful, such as an equation using mathjax:

$$
E = mc^2
$$

To reference a citation you can add your `.bib` file to the working directory and name it in the YAML metadata or generate an automated one as done here, then you only need to reference the label value in the `.bib` file. For example this package is built on top of the wonderful {pagedown} package and I will cite it at the end of this sentance using this in the rmd `[@R-pagedown]` [@R-pagedown].

To get a better understanding of how to include features like these please refer to the {posterdown} [wiki](https://github.com/posterdown/wiki).

**_Now on to the results!_**

# Results

Here you may have some figures to show off, bellow I have made a scatterplot with the infamous Iris dataset and I can even reference to the figure automatically like this, `Figure \@ref(fig:irisfigure)`, Figure \@ref(fig:irisfigure).

```{r, irisfigure, fig.cap='Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="80%"}
par(mar=c(2,2,0,1))
plot(x = iris$Sepal.Length, y = iris$Sepal.Width,
     col = iris$Species, pch = 19, xlab = "Sepal Length",
     ylab = "Sepal Width")
```

Maybe you want to show off some of that fancy code you spent so much time on to make that figure, well you can do that too! Just use the `echo=TRUE` option in the r code chunk options, Figure \@ref(fig:myprettycode)!

```{r myprettycode, echo=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=6, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

How about a neat table of data? See, Table \@ref(tab:iristable):

```{r, iristable}
knitr::kable(
  iris[1:15,1:5], format = "html",
  caption = "A table made with the **knitr::kable** function.",
  align = "c", col.names = c("Sepal <br> Length",
                             "Sepal <br> Width",
                             "Petal <br> Length",
                             "Petal <br> Width",
                             "Species"),
  escape = FALSE)
```

# Conclusion
In this work we presented an integrated visual analytics dashboard for public and government analysis of tracking data, history of credit card, loyalty card and social media data. Multiple text mining, visualisation techniques were applied to further investigate things happened in Abila city in 2014. Abnormal behaviors were discovered. 

# Acknowledgement 

The authors would like to thank Professor Kam Tin Seong for his kind support and guidance on the project. 



